\section{What Each One Have Done}

During the development of the project, all team members remained consistently active, as evidenced by the commits made. Every member contributed to all aspects of the game; however, we decided to modularize the code to improve workflow. As a result, some parts of the game were primarily developed by specific team members.

Eric Ribeiro was responsible for the initial structure of the game, including the character physics and the modularization of functions. He also implemented key mechanics, such as the obelisk (used to push the stone blocking the boss gate), camera movement, and the game design for the level (strategically positioning enemies, spikes, and platforms). Additionally, Eric worked on the soundtrack and the score mechanic. Overall, Eric focused on the structural aspects of the game and provided assistance with other functions when necessary.

Lucas Menezes primarily developed the mechanics for the main character, including the weapons (sword, shield, and projectiles), animated the player's actions, and implemented the health bar. He also assisted in sourcing sprites. Furthermore, Lucas actively participated in the development of the menu screens and the implementation of the text elements and made the unittest.

Victor Iwamoto played a key role in defining the game's aesthetic identity, including sprite selection and menu design. He was responsible for developing the mechanics of all bosses and enemies (attacking, movement, and other behaviors), standardizing the sprite implementation method, and compiling the final report.

It's important to note that each member documented the code they contributed.





