\section{Game History}

In ancient times, the Freydis clan was revered for their bravery and skill in hunting legendary beasts. During an epic journey, the most powerful warriors, Erik and Stella, ventured into the ruins of the ancient palaces of Vermont with an impossible mission: to destroy the Three Calamities, mythological creatures of immeasurable power.

Balrog, the Lightning God, Ganon, the Indestructible, and Demogorgon, the Winter Demon, were responsible for the chaos and destruction that plagued the region. Though their courage was unwavering, Erik and Stella succumbed to the devastating power of the Calamities, their bodies consumed by the shadows of the beasts. With the death of the heroes, the palace door was sealed with mystical powers, as a warning: no living being could ever dare to challenge those terrible entities again.

Centuries passed, and the legend of the Three Calamities was nearly forgotten. However, in the present era, a new hero emerges: August, a direct descendant of the Freydis clan. Through an inexplicable phenomenon, he inherits the abilities of his ancestors, able to transform into them and access their powers to continue the unfinished mission of vengeance and redemption. His journey will be arduous and filled with challenges, as he will face monsters with unique abilities, which can only be defeated with the help of the spirits of his ancestors.

To break the seal of the Vermont palace and finally face the Three Calamities, August must locate the Obelisk of Eldrith, a mysterious artifact capable of breaking the ancient magic that protects the palace. However, the path to the Obelisk is long and filled with immense dangers, and the young hero will need to master the powers of his ancestors to overcome these obstacles and reclaim the lost honor of his clan.

Will August be able to honor his family’s legacy, defeat the Three Calamities, and restore the greatness of the Freydis? Only fate will tell.